Kindly Bent to Free Us

### 2019-07-02 kindly/lang.tex
Adjusts the kinding rules a little bit.

\begin{figure}[ht]
  \centering
  \input{infer/sd-kinds}
  \caption{Syntax-directed kind inference --
    $\inferSK{C}{\E}{\tau}{(\Multi k)k}$}
  \label{rules:sd-kinding}
\end{figure}

>>>>

We note $\inferSK{C}{\E}{\tau}{(\Multi k)k}$
when $\tau$ has kind $(\Multi k)k$ in environment $\E$ under constraints $C$.
The rules are shown in \cref{rules:sd-kinding}.
Kinds and types follow a small calculus with variables ($\tvar$,\dots),
functions (type constructors $\T{t}$), application ($\tapp{t}{\Multi{\tau}}$)
and primitives such as arrow ($\tau\tarr{k}\tau'$) and
borrow ($\borrowty{k}{\tau}$).
Kind inference is thus fairly straightforward and is done simply by following
the syntax of the types. The only kind arrows can appear when looking
up the kind scheme of a type constructor $\T t$. Kind arrows are forbidden
in any other contexts.

\begin{figure}[ht]
  \centering
  \input{infer/sd-kinds}
  \caption{Syntax-directed kinding rule --
    $\inferSK{C}{\E}{\tau}{k}$}
  \label{rules:sd-kinding}
\end{figure}
